Different rules for binocular combination of luminance flicker in cortical and subcortical pathways

### 2023-06-22 manuscript.Rmd
Testing auto-download of appendix data

processdata <- 3  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping
# 3 - download all raw data and analyse (requires 48GB of storage)
cleanupraw <- 1  # if downloading raw data, delete once processed to save space

@@

# (download and) analyse individual participant data for replication expt

@@

         # then unzip the tar file
         untar(paste0(rawdir,'P',200+participant,'.tar'),exdir=paste0(rawdir,'P',100+participant))

>>>>

processdata <- 1  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all figures
# 1 - generate figures using the processed group data
# 2 - average data across participants, do bootstrapping
# 3 - download all raw data and analyse (requires 48GB of storage)
cleanupraw <- 1  # if downloading raw data, delete once processed to save space

@@

# (download and) analyse individual participant data for replication expt
processdata <- 3

@@

         # then unzip the tar file
         untar(paste0(rawdir,'P',200+participant,'.tar'),exdir=paste0(rawdir,'P',200+participant))
